Commit Rater

### 2015-08-24 presentations/paper/methodology.tex
Add TODOs to Data ExtractionÂ

This metamodel is concerned with MSR papers. Thus, the methodology
section would be reasonably subdivided into the three major phases of
an MSR research project.

The subsection on data extraction is concerned with issues like the
following:

\begin{itemize}
\item What repository was chosen and why?
\item What sort of extraction techniques is applied?
\item What sort of extra processing (e.g., filtering) is applied?
\item What constraints were chosen to help with scalability?
\end{itemize}

>>>>

% This metamodel is concerned with MSR papers. Thus, the methodology
% section would be reasonably subdivided into the three major phases of
% an MSR research project.
%
% The subsection on data extraction is concerned with issues like the
% following:
%
% \begin{itemize}
% \item What repository was chosen and why?
% \item What sort of extraction techniques is applied?
% \item What sort of extra processing (e.g., filtering) is applied?
% \item What constraints were chosen to help with scalability?
% \end{itemize}

% TODO: Describe extraction process
% TODO: Describe preprocessing and output
% TODO: Mention commit-limit
% TODO: Introduce example repos
